On Secure Delegation of SampBQP with a Classical Client

### 2020-02-07 bqp.tex
Write theorem on BQP key obsv

\Ethan{Just syntax of QFHE in the preliminary; move the theorem here}

@@

>>>>

@@

\begin{thm}
	\label{decodeMeasureOrder}
	Let $sk$ be some secret key of $\mathsf{QHE}$.
	Let $n\in\bbN$.
	Let $m\in\bbN$ be the length of the ciphertexts under $\mathsf{QHE}$ corresponding to plaintexts of length $n$.
	Let $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_n$, where each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement.

	There exists $\Lambda'=\Lambda'_1\otimes\ldots\otimes\Lambda'_m$ where each $\Lambda_i'$ is a single-qubit $X$ or $Z$ measurement, and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that:
	$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{thm}
\begin{proof}
	This is a proof by construction.
	We require $\Lambda'$ and $\widehat{\mathsf{QHE.Dec}}$ such that $\forall\sigma=(X^xZ^z\rho Z^zX^x, c_{x,z})$,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'(\sigma)$$

	Clearly,
	$$\Lambda\circ\mathsf{QHE.Dec}(\sigma)=\Lambda(\rho)$$

	Let $\Lambda'$ applies $\Lambda$ to the first register, getting $ct=\Lambda(X^xZ^z\rho Z^zX^x)$, and applies computational basis measurement to the second register, getting $c_{x, z}$.

	Note that the Pauli one-time pad on $ct$ commutes with $X$ and $Z$ measurements.
	So let $\widehat{\mathsf{QHE.Dec}}$ decode $c_{x, z}$ to get $(x, z)$ and undo the one-time pad on $ct$ to get $\Lambda(\rho)$.
\end{proof}

### 2020-02-07 preliminaries.tex
Add notes from Skype discussion
Add another note from Skype discussion
Write theorem on BQP key obsv

We define a few relevant complexity classes. \Ethan{Do we need to define $\BPP$ and $\BQP$ too?}

@@

\begin{dfn}
	$\FBQP$ is the functional analogue of the class $\BQP$. That is, every instance corresponds to a string rather than a yes/no bit. The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
\end{dfn}

@@

\subsection{Semantic security for interactive protocols}

@@

The quantum homomorphic encryption scheme in \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients as below:

\begin{thm}
	\label{decodeMeasureOrder}
	There exists a QFHE $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$ with the following extra properties:
	\begin{itemize}
		\item $\mathsf{QHE.Keygen}$ can be done classically.
		\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
		\item \Ethan{Is this obvious from the construction or do we need proof here?} Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists product of $X$ and $Z$ measurements $\Lambda'$ and $\BPP$ algorithm $\widehat{\mathsf{QHE.Dec}}$ such that
			$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
	\end{itemize}
\end{thm}

>>>>

We define a few relevant complexity classes.

\Ethan{TODO Dfn $\BQP$}
\Ethan{TODO Negligible errors}

@@

\begin{dfn}
    \Ethan{TODO Negligible errors}
	$\FBQP$ is the functional analogue of the class $\BQP$. That is, every instance corresponds to a string rather than a yes/no bit. The error probability is still bounded above away from $\fot$ for some uniform quantum circuit family.
\end{dfn}

@@

\subsection{Semantic security for interactive protocols}
\Ethan{Just call this blindness and put this under interactive protocols}

@@

The quantum homomorphic encryption scheme $\mathsf{QHE}$ from \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
	\item Its ciphertext takes the form $(X^xZ^z\ket\rho Z^zX^x, c_{x, z})$, where $\rho$ is the plaintext and $c_{x, z}$ is a ciphertext that decodes to $(x, z)$ under a certain classical homomorphic encryption scheme.
	We assume without loss of generality that the length of $c_{x, z}$ is only dependent on the length of $\ket\phi$ by padding $0$s if necessary.
\end{itemize}
